---
title: "Programming Assignment 9-4"
author: "Peter Gajda"
date: "8 December 2019"
output: ioslides_presentation
widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Programming Assignment 9-4 - Shiny App

This is a presentation for the Coursera Data Class "Developing Data products".
The objective of the class was to write a shiny app.
The app which was created is based on the iris dataset. The goal ist to give the
user the opportunity to create a plot with to different variables from the iris
dataset. The plot automatically creates to lines. One line is fixed and represents
a linear model. The other lines lowess ist configurable via the app.
The following slides show the R code for the ui and server side and on the last slide
an example of one possible configuration of the plot is shown.

- The application can be found in the following link
- https://petergajda.shinyapps.io/ProgrammingAssignment_9-4/

- The source code is hosted in the following link
- https://github.com/petergajda/ProgrammingAssignment_9-4


## ui.R - Configuration

```{r, echo = TRUE, warning = FALSE, message=FALSE, eval=FALSE}
library(datasets)
fluidPage(    
  titlePanel("Iris Data Set"),
  sidebarLayout(      
    sidebarPanel(
      selectInput("option1", "Option Y-Axis:", choices=colnames(iris[1:4])),
      selectInput("option2", "Option X-Axis:", choices=colnames(iris[1:4])),
      hr(), 
      helpText("Data from iris data set (1936)."),
      hr(),
      sliderInput("lowess", "Line lowess:", min = 0.01, max = 1, value = 0.5),
      hr(),
      helpText("Please use this app to create...")
      ),
    mainPanel(
      plotOutput("irisPlot")  
    )
  )
)
```



## server.R - Configuration

```{r, echo = TRUE, warning = FALSE, message=FALSE, eval=FALSE}
library(datasets)
function(input, output) {
 output$irisPlot <- renderPlot({
    plot(iris[,input$option1] ~ iris[,input$option2],
            main=paste("This graph shows", input$option1, "by", input$option2),
            pch = 3,
            ylab=input$option1,
            xlab=input$option2,
            col=c("red", "green", "blue"))
         abline(lm(iris[,input$option1] ~ iris[,input$option2]), col="black", 
                lwd=3, lty=4)
         lines(lowess(iris[,input$option1] ~ iris[,input$option2],
                      f = input$lowess), col = 'black', lwd=3, lty=4)
         legend('topright', legend = unique(iris$Species), 
                col = c("red", "green", "blue"), pch = 3)
```

Via iris[,input$option1] or iris[,input$option2] the app gets the information which column from the iris dataset has to be used.
Via input$lowess in the f argument in the lines function the app gets the information about the lowess level.


## Plot: Sepal.Length vs. Sepal.Width {.flexbox .vcenter}

```{r, echo = FALSE, warning = FALSE, message=FALSE}

    plot(iris$Sepal.Length ~ iris$Sepal.Width,
            main=paste("This graph shows Sepal.Length by Sepal.Width"),
            pch = 3,
            col=c("red", "green", "blue"))
         abline(lm(iris$Sepal.Length ~ iris$Sepal.Width), col="black", lwd=3, lty=4)
         lines(lowess(iris$Sepal.Length ~ iris$Sepal.Width, f = 0.5), col = 'black', lwd=3, lty=4)
         legend('topright', legend = unique(iris$Species), col = c("red", "green", "blue"), pch = 3)
```



